Custom Figure Generation

### 2023-03-15 R/CustomFigureGeneration.rmd
Create CustomFigureGeneration.rmd
This notebook serves as a way to create variations on the figures from the PaperFigureGeneration notebook. (e.g. compressing a plot for a poster).

---
title: "Paper Figure Generation"
author: "Ben Morledge-Hampton"
date: "6/21/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

@@

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
               fig.path = paste0(file.path("deamination_analysis_output","paper_figures"),
                                 .Platform$file.sep))

@@

```{r read_figure_1_data}
NHF1CPDMismatchDataAllReps = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDMismatchDataAllReps)) {
  NHF1CPDMismatchDataAllReps[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(NHF1CPDMismatchDataAllReps)[i]
  ))
}
```

```{r figure_1B}
plotMismatchTypeFrequencies(NHF1CPDMismatchDataAllReps$`1h`, ylim = c(0,0.8),
                            title = "NHF1 CPD 1h All Reps Mismatch Type Frequencies")
```
```{r figure_1C}
print("NHF1 CPD 1h all reps C>T mismatch dipyrimidine context frequency:")
plotTrinucleotideContext(NHF1CPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
                         title = "NHF1 CPD 1h All Reps C>T Mismatch Trinuc Context",
                         printDipyFreq = TRUE)
```
```{r figure_1D}
plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
                                title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Frequencies",
                                xAxisBreaks = c(-1,-10,-20,-30))
```

```{r read_figure_2_data}
NHF1CPDMMFreqZScoresAllReps = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDMMFreqZScoresAllReps)) {
  NHF1CPDMMFreqZScoresAllReps[[i]] = fread(generateFilePath(
    directory = NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(NHF1CPDMMFreqZScoresAllReps)[i], includedMismatches = c("C>T")
  ))
}

NHF1FivePrimeMismatchCPDNucFreqAllReps = fread(generateFilePath(
  directory = NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
  strandPolarity = "five_prime", anchored = TRUE
))

NHF1CPDTGGSeqFreqAllReps = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDTGGSeqFreqAllReps)) {
  NHF1CPDTGGSeqFreqAllReps[[i]] = fread(generateFilePath(
    directory = NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(NHF1CPDTGGSeqFreqAllReps)[i], sequence = "TGG"
  ))
}
```

```{r figure_2A, fig.width = 5, fig.height = 6}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllReps["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Freq",
                                         yAxisLabel = "Relative C>T Frequency",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllReps,
                                         xAxisBreaks = c(-1,-10,-20,-30))

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllReps, includedTypes = c("C>T"),
#                                          title = "NHF1 CPD All Reps C>T Mismatch Pos Freq",
#                                          yAxisLabel = "Relative C>T Frequency",
#                                          zScoreTables = NHF1CPDMMFreqZScoresAllReps)
```
```{r figure_2B, fig.width = 6.5, fig.height = 6}
### Just the 1h timepoint ###
plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h All Reps 5' Anchored Nuc Freq",
                               secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
                               xAxisLabel = "Mismatch Relative Position", positionOffset = -1)

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps, 
#                                title = "NHF1 CPD All Reps 5' Anchored Nuc Freq",
#                                secondaryYAxisLabel = "3' Cut Site Distance",
#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
#                                xAxisLabel = "Mismatch Relative Position")
```
```{r figure_2C, fig.width = 5, fig.height = 6}
### Just the 1h timepoint ###
plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps$`1h`, title = "NHF1 CPD 1h All Reps General Read TGG Freq",
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE, querySequences = c("TGG"),
                        expansionOffset = 10, minReadLength = 20, maxReadLength = 27, positionOffset = 10,
                        yAxisLabel = "TGG Trinucleotide Frequency", defaultColor = "Black")

### All timepoints together ###
# plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps, title = "NHF1 CPD All Reps General Read TGG Freq",
#                         showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE, querySequences = c("TGG"),
#                         expansionOffset = 10, minReadLength = 21, maxReadLength = 27,
#                         yAxisLabel = "TGG Trinucleotide Frequency", defaultColor = "Black")
```

```{r read_figure_3_data}
NHF1CPDMismatchDataAllRepsTGGFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDMismatchDataAllRepsTGGFiltered)) {
  NHF1CPDMismatchDataAllRepsTGGFiltered[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1CPDMismatchDataAllRepsTGGFiltered)[i],
    repitition = "all_reps", filtering = "TGG_filtered"
  ))
}

arabidopsisCPDMismatchDataAllRepsFiltered = arabidopsisCPDTimepoints
for (i in seq_along(arabidopsisCPDMismatchDataAllRepsFiltered)) {
  arabidopsisCPDMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "Arabidopsis", lesion = "CPD", timepoint = names(arabidopsisCPDMismatchDataAllRepsFiltered)[i],
    repitition = "all_reps", filtering = "TGG_filtered"
  ))
}

yeastCPDMismatchDataAllRepsFiltered = yeastCPDTimepoints
for (i in seq_along(yeastCPDMismatchDataAllRepsFiltered)) {
  yeastCPDMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
    yeastSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "yeast", lesion = "CPD", timepoint = names(yeastCPDMismatchDataAllRepsFiltered)[i],
    repitition = "all_reps", filtering = "TGG_filtered"
  ))
}

NHF1CPDMMFreqZScoresAllRepsTGGFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDMMFreqZScoresAllRepsTGGFiltered)) {
  NHF1CPDMMFreqZScoresAllRepsTGGFiltered[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
    timepoint = names(NHF1CPDMMFreqZScoresAllRepsTGGFiltered)[i], includedMismatches = c("C>T")
  ))
}

arabidopsisCPDMMFreqZScoresAllRepsFiltered = arabidopsisCPDTimepoints
for (i in seq_along(arabidopsisCPDMMFreqZScoresAllRepsFiltered)) {
  arabidopsisCPDMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
    cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
    timepoint = names(arabidopsisCPDMMFreqZScoresAllRepsFiltered)[i], includedMismatches = c("C>T")
  ))
}

yeastCPDMMFreqZScoresAllRepsFiltered = yeastCPDTimepoints
for (i in seq_along(yeastCPDMMFreqZScoresAllRepsFiltered)) {
  yeastCPDMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
    yeastSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
    cellType = "yeast", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
    timepoint = names(yeastCPDMMFreqZScoresAllRepsFiltered)[i], includedMismatches = c("C>T")
  ))
}

NHF1CPDGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
for (i in seq_along(NHF1CPDGroupedStatsAllRepsFiltered)) {
  NHF1CPDGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
    strandPolarity = names(NHF1CPDGroupedStatsAllRepsFiltered)[i]
  ))
}

@@

```{r figure_3A, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGGFiltered,
                                         yAxisLabel = "Relative C>T Frequency", xAxisBreaks = c(-1,-10,-20,-30))
plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["ZT2"], includedTypes = c("C>T"),
                                         title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
                                         yAxisLabel = "Relative C>T Frequency", xAxisBreaks = c(-1,-10,-20,-30))
plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
                                         title = "Yeast CPD 20min All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
                                         yAxisLabel = "Relative C>T Frequency", xAxisBreaks = c(-1,-10,-20,-30))

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered, includedTypes = c("C>T"),
#                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGGFiltered,
#                                          yAxisLabel = "Relative C>T Frequency")
# plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
#                                          yAxisLabel = "Relative C>T Frequency")
# plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
#                                          yAxisLabel = "Relative C>T Frequency")
```
```{r figure_3B, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGGFiltered,
                                         posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency",
                                         xAxisBreaks = c(1,10,20,30))
plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["ZT2"], includedTypes = c("C>T"),
                                         title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
                                         posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency",
                                         xAxisBreaks = c(1,10,20,30))
plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
                                         title = "Yeast CPD 20min All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
                                         posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency",
                                         xAxisBreaks = c(1,10,20,30))

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered, includedTypes = c("C>T"),
#                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGGFiltered,
#                                          posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
# plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
#                                          posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
# plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
#                                          posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
```
```{r figure_3C, fig.width = 7.5, fig.height = 5}
### Just the 1h timepoint ###
plotGroupedPositionStats(NHF1CPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
                         NHF1CPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
                         POS_DIFF, title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
                         xAxisBreaks = c(22:30))

plotGroupedPositionStats(arabidopsisCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "ZT2"],
                         arabidopsisCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "ZT2"],
                         POS_DIFF, title = "Arabidopsis CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
                         xAxisBreaks = c(24:30))

plotGroupedPositionStats(yeastCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "20min"],
                         yeastCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "20min"],
                         POS_DIFF, title = "Yeast CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
                         xAxisBreaks = c(22:25))

@@

```{r read_figure_4_data}
NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
  strandPolarity = "three_prime", anchored = TRUE, filtering = "TGG_filtered"
))
NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
  NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1ExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "HYV", filtering = "TGG_filtered"
  ))
}

NHF1GeneralReadsCPDNucFreqAllReps1hFilteredCombined = fread(generateFilePath(
  NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
  cellType = "NHF1", lesion = "CPD", repitition = "all_reps", timepoint = "1h",
  filtering = "TGG_filtered", additionalInformation = "combined_read_lengths"
))
NHF1GeneralReadsCPDSeqFreqAllReps1hFilteredCombined = fread(generateFilePath(
  NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "NHF1", lesion = "CPD", timepoint = "1h", repitition = "all_reps",
  sequence = "HYV", filtering = "TGG_filtered", additionalInformation = "combined_read_lengths"
))
arabidopsisGeneralReadsCPDSeqFreqAllRepsZT2FilteredCombined = fread(generateFilePath(
  arabidopsisGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "Arabidopsis", lesion = "CPD", timepoint = "ZT2",
  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered",
  additionalInformation = "combined_read_lengths"
))
yeastGeneralReadsCPDSeqFreqAllReps20MinFilteredCombined = fread(generateFilePath(
  yeastGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "yeast", lesion = "CPD", timepoint = "20min",
  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered",
  additionalInformation = "combined_read_lengths"
))
EColiGeneralReadsCPDSeqFreqAllReps5MinFilteredCombined = fread(generateFilePath(
  EColiGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "E_coli_WT", lesion = "CPD", timepoint = "5min",
  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered",
  additionalInformation = "combined_read_lengths"
))
```

```{r figure_4A, fig.width = 6.5, fig.height = 6}
plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored Nuc Freq",
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = FIVE_PRIME, showFivePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 19, maxReadLength = 25,
                               xAxisLabel = "Mismatch Relative Position", positionOffset = 1)
```
```{r figure_4B, fig.width = 5, fig.height = 6}
# ### Just the 1h timepoint (asterisks) ###
# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
#                         title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored HYV Freq",
#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
#                         showFivePrimeCutSite = TRUE, querySequences = c("333"),
#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 6,
#                         endBasedCheckPositions = -9, xAxisLabel = "Mismatch Relative Position",
#                         significanceAsteriskBreakpoints = c(1e-3, 1e-10, 1e-20))

## Just the 1h timepoint (full p-values) ###
plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
                        title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored HYV Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 6,
                        endBasedCheckPositions = -9, displayPValue = FALSE, xAxisLabel = "Mismatch Relative Position",
                        xAxisBreaks = c(-2,-10,-20,-30), xlim = c(-35, -4))

### All timepoints together ###
# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
#                         title = "NHF1 CPD All Reps TGG-Filtered 3' Anchored YR Freq",
#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
#                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
#                         endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
```
```{r figure_4C, fig.width = 6.5, fig.height = 4.75}
plotNucFreqVsReadLengthBarPlot(NHF1GeneralReadsCPDNucFreqAllReps1hFilteredCombined[Position <= 7], 
                               title = "NHF1 CPD 1h All Reps TGG-Filtered Nuc Freq",
                               secondaryYAxisLabel = "Read Length", ylim = c(0,1),
                               posType = FIVE_PRIME, showFivePrimeCutSite = TRUE,
                               expansionOffset = 10, xAxisBreaks = c(-9,0,7),
                               xAxisLabel = "5' Relative Position")
```
```{r figure_4D, fig.width = 5, fig.height = 4}
plotSequenceFrequencies(NHF1GeneralReadsCPDSeqFreqAllReps1hFilteredCombined[Position <= 7],
                        title = "NHF1 CPD 1h All Reps TGG-Filtered General Reads HYV Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
                        expansionOffset = 10, backgroundPositions = -9:-4,
                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
                        xAxisBreaks = c(-8, 0, 8), ylimMax = 0.6, ylimMaxModifier = 1)
```
```{r figure_4E, fig.width = 5, fig.height = 4}
plotSequenceFrequencies(arabidopsisGeneralReadsCPDSeqFreqAllRepsZT2FilteredCombined[Position <= 7],
                        title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered General Reads HYV Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
                        expansionOffset = 10, backgroundPositions = -9:-4,
                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
                        xAxisBreaks = c(-8, 0, 8), ylimMax = 0.6, ylimMaxModifier = 1)
```
```{r figure_4F, fig.width = 5, fig.height = 4}
plotSequenceFrequencies(yeastGeneralReadsCPDSeqFreqAllReps20MinFilteredCombined[Position <= 7],
                        title = "Yeast CPD 20min All Reps TGG-Filtered General Reads HYV Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
                        expansionOffset = 10, backgroundPositions = -9:-4,
                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
                        xAxisBreaks = c(-8, 0, 8), ylimMax = 0.6, ylimMaxModifier = 1)
```
```{r figure_4G, fig.width = 5, fig.height = 4}
plotSequenceFrequencies(EColiGeneralReadsCPDSeqFreqAllReps5MinFilteredCombined[Position <= 5],
                        title = "E. coli CPD 5min All Reps TGG-Filtered General Reads HYV Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
                        expansionOffset = 10, xAxisLabel = "5' Relative Position",
                        xlim = c(-9,7), xAxisBreaks = c(-8, 0, 6), ylimMax = 0.6, ylimMaxModifier = 1)
```

```{r read_figure_5_data}
# Note: This file was created manually by combining/modifying a couple different files counting tandem mismatches.
NHF1TandemMismatchCountsComparisonAllReps = fread(generateFilePath(
  NHF1MismatchesByReadDataDirectory, dataTypeStrings$tandemMismatchCountsComparison, ".tsv",
  cellType = "NHF1", repitition = "all_reps"
))
```

```{r figure_5B, fig.width = 8, fig.height = 5}
NHF1TandemMismatchCountsComparisonAllReps = NHF1TandemMismatchCountsComparisonAllReps[
  Lesion == "CPD" & Timepoint == "1h"
]
print(
    ggplot(NHF1TandemMismatchCountsComparisonAllReps, aes(Mismatch_Type, Tandem_Mismatches_Count, fill = Search_Method)) +
      geom_bar(stat = "identity", position = "dodge") +
      labs(title = "NHF1 CPD 1h All Reps Tandem Mismatch Counts", x = "Mismatch Type", y = "Tandem Mismatch Count") +
      geom_text(aes(label=Tandem_Mismatches_Count), position = position_dodge(width = 0.9), vjust = -0.25, size = 5) +
      blankBackground + defaultTextScaling + scale_fill_brewer(palette = "Set1") +
      coord_cartesian(ylim = c(0,200000), expand = FALSE)
  )
```

```{r read_figure_6_data}
NHF1CPDCCtoTTMismatchDataAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDCCtoTTMismatchDataAllRepsFiltered)) {
  NHF1CPDCCtoTTMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    filtering = "TGG_filtered", includedMismatches = "CC>TT",
    timepoint = names(NHF1CPDCCtoTTMismatchDataAllRepsFiltered)[i]
  ))
}

NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered)) {
  NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
    directory = NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    filtering = "TGG_filtered", includedMismatches = "CC>TT",
    timepoint = names(NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered)[i]
  ))
}

NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllReps1hFiltered = fread(generateFilePath(
    NHF1ExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv", timepoint = "1h",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", includedMismatches = "CC>TT",
    strandPolarity = "three_prime", anchored = TRUE, sequence = "HYV", filtering = "TGG_filtered",
))

NHF1CPDCCToTTGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
for (i in seq_along(NHF1CPDCCToTTGroupedStatsAllRepsFiltered)) {
  NHF1CPDCCToTTGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
    strandPolarity = names(NHF1CPDCCToTTGroupedStatsAllRepsFiltered)[i], includedMismatches = "CC>TT"
  ))
}

arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
for (i in seq_along(arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered)) {
  arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
    cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
    strandPolarity = names(arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered)[i], includedMismatches = "CC>TT"
  ))
}

yeastCPDCCToTTGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
for (i in seq_along(yeastCPDCCToTTGroupedStatsAllRepsFiltered)) {
  yeastCPDCCToTTGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
    yeastSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
    cellType = "yeast", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
    strandPolarity = names(yeastCPDCCToTTGroupedStatsAllRepsFiltered)[i], includedMismatches = "CC>TT"
  ))
}
```

>>>>

---
title: "Custom Figure Generation"
author: "Ben Morledge-Hampton"
date: "6/21/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

@@

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
               fig.path = paste0(file.path("deamination_analysis_output","custom_figures"),
                                 .Platform$file.sep))

@@

```{r read_custom_figure_3_data}
NHF1CPDGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
for (i in seq_along(NHF1CPDGroupedStatsAllRepsFiltered)) {
  NHF1CPDGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
    strandPolarity = names(NHF1CPDGroupedStatsAllRepsFiltered)[i]
  ))
}

@@

```{r figure_3C, fig.width = 8, fig.height = 3}
### Just the 1h timepoint ###
plotGroupedPositionStats(NHF1CPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
                         NHF1CPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
                         POS_DIFF, title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
                         xAxisBreaks = c(22:30), yAxisTitle = "Pos Diff")

plotGroupedPositionStats(arabidopsisCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "ZT2"],
                         arabidopsisCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "ZT2"],
                         POS_DIFF, title = "Arabidopsis CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
                           xAxisBreaks = c(24:30), yAxisTitle = "Pos Diff")

plotGroupedPositionStats(yeastCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "20min"],
                         yeastCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "20min"],
                         POS_DIFF, title = "Yeast CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
                         xAxisBreaks = c(22:25), yAxisTitle = "Pos Diff")

@@
